Supporting Information to Estimating the Initial Susceptible Fraction in Dengue Dynamics"

### 2014-12-02 S1_lm1.tex
fixed many subtle bugs in the stochastic model

 \caption{Block diagram detailing the stochastic model}
 \label{fig:sde_blocks}
\end{figure}

@@

The possible state-transitions and their  propensities are listed in table 
\ref{tab:trans}.
\begin{table}
\caption{
\bf{State-transitions and propensities: $P(\Delta X(t)|X(t))$}. The 
transitions are summarized below, Fully expanded the system comtemplates 64 
possible state transitions, as can be verified in figure \ref{fig:sde_blocks}. 
}
\label{tab:trans}
\begin{center}
\begin{tabular}[c]{l|l|l|l}
\hline
Transition & Propensity & State Change & Description\\
\hline
$S \rightarrow I_i$ & $\beta S I_{*i}$ & $\Delta S(t)=-1,\, \Delta I_i(t) = 1$ 
& Primary infection \\
$I_i \rightarrow R_i$ & $\sigma I_i$ & $\Delta I_i(t)=-1,\, \Delta R_i(t) = 1$ 
& Primary recovery\\
$R_i \rightarrow I_{[i]j}$ & $\beta \delta R_i I_{*j}$ & $$\Delta R_i(t)=-1,\, 
\Delta I_{[i]j}(t) = 1$$ & Secondary infection\\
$I_{[i]j} \rightarrow R_{ij}$ & $\sigma I_{[i]j}$ &$$\Delta I_{[i]j}(t)=-1,\, 
\Delta R_{ij}(t) = 1$$& Secondary recovery\\
$R_{ij} \rightarrow I_{[ij]k}$ & $\beta \delta R_{ij} I_{*k}$ & Tertiary 
infection\\
$I_{[ij]k} \rightarrow R_{ijk}$ & $\sigma I_{[ij]k}$ & Tertiary recovery\\
$R_{ijk} \rightarrow I_{[ijk]l}$ & $\beta \delta R_{ijk} I_{*l}$ & Quaternary 
infection\\
$I_{[ijk]l} \rightarrow R_{ijkl}$ & $\sigma I_{[ijk]l}$ & Quaternary recovery\\
$\rightarrow S$ & $\mu N$ & Birth\\
$All \rightarrow$ & $\mu N$ & Death\\
\hline
\end{tabular}
\end{center}

@@

The model is implemented as a continuous time Markov jump process. Let
$$\overrightarrow{X}(t) = [S(t), I_1(t), I_2(t), \ldots, R_{1234}(t)]$$ 
be the 
state of the system at the time $t$. 
The system is written as a forward Kolmogorov differential equation, which in 
matrix form looks like
\begin{equation}
dP_X(t) = Q P_X(t) 
\end{equation}

>>>>

 \caption{Block diagram detailing the stochastic model. Infected individuals 
with different Dengue viruses are represented by different colors. Infections 
are also represented by colored arrows matching the virus type.}
 \label{fig:sde_blocks}
\end{figure}

@@

The possible state-transitions and their  propensities are listed in table 
\ref{tab:trans}.
\begin{table}
\caption{
\bf{State-transitions and propensities: $P(\Delta X(t)|X(t))$}. The 
transitions are summarized below. Fully expanded, the system contemplates 64 
possible state transitions, as can be verified in figure \ref{fig:sde_blocks}. 
}
\label{tab:trans}
\begin{center}
\begin{tabular}[c]{l|l|l|l}
\hline
Transition & Propensity & State Change & Description\\
\hline
$S \rightarrow I_i$ & $\beta S I_{*i}$ & $\Delta S(t)=-1,\, \Delta I_i(t) = 1$ 
& Primary infection \\
$I_i \rightarrow R_i$ & $\sigma I_i$ & $\Delta I_i(t)=-1,\, \Delta R_i(t) = 1$ 
& Primary recovery\\
$R_i \rightarrow I_{[i]j}$ & $\beta \delta R_i I_{*j}$ & $\Delta R_i(t)=-1,\, 
\Delta I_{[i]j}(t) = 1$ & Secondary infection\\
$I_{[i]j} \rightarrow R_{ij}$ & $\sigma I_{[i]j}$ &$\Delta I_{[i]j}(t)=-1,\, 
\Delta R_{ij}(t) = 1$& Secondary recovery\\
$R_{ij} \rightarrow I_{[ij]k}$ & $\beta \delta R_{ij} I_{*k}$ &$\Delta 
R_{ij}(t)=-1,\, \Delta I_{[ij]k}(t) = 1$& Tertiary infection\\
$I_{[ij]k} \rightarrow R_{ijk}$ & $\sigma I_{[ij]k}$ &$\Delta 
I_{[ij]k}(t)=-1,\, \Delta R_{ijk}(t) = 1$& Tertiary recovery\\
$R_{ijk} \rightarrow I_{[ijk]l}$ & $\beta \delta R_{ijk} I_{*l}$ &$\Delta 
R_{ijk}(t)=-1,\, \Delta I_{[ijk]l}(t) = 1$& Quaternary infection\\
$I_{[ijk]l} \rightarrow R_{ijkl}$ & $\sigma I_{[ijk]l}$ & $\Delta 
I_{[ijk]l}(t)=-1,\, \Delta R_{ijkl}(t) = 1$ & Quaternary recovery\\
$\rightarrow S$ & $\mu N$ & $\Delta S = 1$ & Birth\\
$All \rightarrow$ & $\mu N$ &$\Delta All = -1$& Death\\
\hline
\end{tabular}
\end{center}

@@

The model is implemented as a continuous time Markov jump process. Let
$$\overrightarrow{X}(t) = [S(t), I_1(t), I_2(t), \ldots, R_{1234}(t)]$$ 
be the 
state of the system at the time $t$. 
The system is written as a forward Kolmogorov differential equation, which in 
matrix form looks like
\begin{equation}
\frac{dP_X(t)}{dt} = Q P_X(t) 
\end{equation}
